Footpath Planning for Example-driven Procedural Road Networks

### 2020-04-13 paper/paper.tex
Fix report figures

\begin{figure}[H]
\centering
\includegraphics[height=0.5\textheight]{img_match_1_1}
\caption{An example of a 1:1 building match, where the sought-after building was found both in the OSM (red) and SLU (blue) datasets.}
\label{fig:space}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[height=0.5\textheight]{img_match_1_n}
\caption{An example of a 1:n building match, where the sought-after building was represented as one polygon in the OSM (red) dataset, but divided into many smaller lots in the SLU (multicolored) dataset.}
\label{fig:space}
\end{figure}

@@

% TODO: Turning function example figure for a polygon

@@

% TODO: building match figures in a horisontal grid
% TODO: figure with buildings-slu-cropped
% TODO: mention utility buildings inside compounds, source of marginal errors

@@

\begin{figure}[H]
\centering
\includegraphics[height=0.5\textheight]{img_turn_function_diff_filled}
\caption{An example of the turning functions of two corresponding buildings, with the area between them highlighted.}
\label{fig:space}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[height=0.5\textheight]{img_pos_error_plot}
\caption{The average positional accuracies per building as a frequency diagram.}
\label{fig:space}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[height=0.5\textheight]{img_turning_function_plot}
\caption{The turning function distances between 1:1 building pairs as a frequency diagram.}
\label{fig:space}
\end{figure}

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{img_building_match}
    \caption{Examples of a 1:1 building match (left), where the sought-after building was found both in the OSM (red) and SLU (blue) datasets, and of a 1:n building match (right), where the sought-after building was represented as one polygon in the OSM (red) dataset, but divided into many smaller lots in the SLU (multicolored) dataset.}
    \label{fig:space}
\end{figure}

@@

@@

% TODO: figure with buildings-slu-cropped
% TODO: mention utility buildings inside compounds, source of marginal errors
% TODO: Turning function example figure for a polygon

% TODO: Update project plan

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{img_turn_function_diff_filled}
    \caption{An example of the turning functions of two corresponding buildings, with the area between them highlighted.}
    \label{fig:space}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{img_pos_error_plot}
    \caption{The average positional accuracies per building as a frequency diagram.}
    \label{fig:space}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{img_turning_function_plot}
    \caption{The turning function distances between 1:1 building pairs as a frequency diagram.}
    \label{fig:space}
\end{figure}
